Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2019-11-26 paper.tex
Added figures, fixed Iain's name

\author{%
  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchirst\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
}

@@

The results for the accuracy and time performance with the proposed audio interface shows an interesting contrast.
That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
However, this trend is almost wholly reversed in the time-to-target results from the Fitts's model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively. 
Since the Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
However, the Fitts's model does not account for changing stimuli and different strategies.
We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target. 
This seems to indicate a speed/accuracy trade-off in finding the targets.
With the Fitts's model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.

>>>>

\author{%
  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchrist\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
}

@@

The results for the accuracy and time performance with the proposed audio interface shows an interesting contrast.
That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively. 
Since Fitts's' model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
However, the Fitts model does not account for changing stimuli and different strategies.
We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target. 
This seems to indicate a speed/accuracy trade-off in finding the targets.
With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
